---
title: "SunsVizOnly"
author: "Adam Rees"
date: "3/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(rvest)
library(dplyr)
require(XML)
require(RCurl)
require(stringr)
require(png)
library(XML)
library(tidyr)
library(MASS)
library(sp)
library(gstat)


library(rapportools)

```


#Things needed for this dataset to work - side of basket shot was taken at
```{r}
sunsgames <- read.csv("~/Desktop/Thesis/ThesisBasketball/sunsgames.csv")

sunsgames <- sunsgames %>% filter(sunsgames$point != 1)

sunsgames$pointsPerShot <- NULL
sunsgames$X_LOC <- NULL
sunsgames$Y_LOC <- NULL
sunsgames$shootingTeam <- NULL

for(i in 1:nrow(sunsgames)){
  sunsgames$X_LOC[i] <- -1 * as.double(sunsgames$baseline[i] * 500)
  sunsgames$Y_LOC[i] <- as.double(sunsgames$sideline[i] * 940)
  sunsgames$pointsPerShot[i] <- as.double(sunsgames$makes[i] * sunsgames$point[i])

}

sunsgames <- sunsgames %>% filter(sunsgames$Y_LOC < 296)

```


```{r}
x1 <- sort(unique(sunsgames$X_LOC))[1:10]
x2 <- sort(unique(sunsgames$Y_LOC))[1:10]

covGen(x1, x2, .47)


xLoc <- x1
yLoc <- x2
lam <- .47
covGen <- function(xLoc, yLoc, lam) {
  # Evaluates mean and covariance of GP at grid of points on [0,1]
  # Inputs:
  # x, y: input and output values of data set
  # lam: smoothing parameter in RBF kernel
  # sig: error standard deviation of y
  # design: grid of points to evaluate the GP
  # Returns:
  # mean=posterior mean, vars=posterior variance, and design=evaluation points
  n <- length(xLoc)*length(yLoc)
  Sigma <- matrix(0,nrow=n, ncol=n)
  
  all <- matrix(0, nrow= n, ncol = 2)
  k <- 1
  for(i in 1:length(xLoc)){
    for(j in 1:length(yLoc)){
      all[k,] <- c(xLoc[i], yLoc[j]) 
      k <- k + 1 
    }
  }

  for (i in 1:nrow(Sigma)) {
    for (j in i:nrow(Sigma))
      Sigma[i,j] <- rbf.k(all[i,], all[j,], lam) -> Sigma[j,i]
  }
  S11 <- Sigma
  S12 <- Sigma
  S21 <- Sigma
  S22 <- Sigma
  
  Sigma <- c(S11, S12, S21, S22)
  return(Sigma)
}


#Next function goes right here
```


```{r}
#The following code is so that we can get n, ppsAve for each location
nvalues <- sunsgames %>% group_by(X_LOC, Y_LOC) %>% count() 
dupShots <- sunsgames %>% left_join(nvalues)

sumShots <- dupShots %>% group_by(X_LOC, Y_LOC) %>% mutate(pps = sum(pointsPerShot))

#Now you have the pps for each location
sunsgames$n <- sumShots$n
sunsgames$ppsAve <- sumShots$pps/sumShots$n

# All of the different locations we will be dealing with
xLocs <- sort(unique(sunsgames$X_LOC))
yLocs <- sort(unique(sunsgames$Y_LOC))


sunsgames %>% arrange(X_LOC, Y_LOC)
sunsgames <- sunsgames %>% distinct(X_LOC, Y_LOC, .keep_all = TRUE) %>% arrange(X_LOC, Y_LOC)


tempY <- c()
tempSig <- c()
counter <- 1

for(i in 1:length(xLocs)){
  for(j in 1:length(yLocs)){
    if(!is.na(sunsgames$X_LOC[counter]) & sunsgames$X_LOC[counter] == xLocs[i] & sunsgames$Y_LOC[counter] == yLocs[j]){
        tempY <- c(tempY, sunsgames$ppsAve[counter])
        tempSig <- c(tempSig, 1/sqrt(sunsgames$n[counter]))
        counter <- counter + 1
    }else{
        tempY <- c(tempY, 0)
        tempSig <- c(tempSig, 1000)
      }
  }
}




```

1632


```{r}
(yLocs)[1:32]
```
295.7334



```{r}

filterOut <- sunsgames[1:14636,]
threePointers <- filterOut %>% filter(point == 3 & Y_LOC < 300 & shooter == 5473)
twoPointers <- filterOut %>% filter(point == 2 & shooter == 5473)


x1Three <- threePointers$X_LOC
x2Three <- threePointers$Y_LOC
yThree <- threePointers$pointsPerShot

x1Two <- twoPointers$X_LOC
x2Two <- twoPointers$Y_LOC
yTwo <- twoPointers$pointsPerShot

#put the if .. 
rbf.k <- function(x,y,sigma)
  return(exp(-1/(2*sigma^2)*(sum((x-y)^2))))

gpreg <- function(x, y, lam, sig, design) {
  # Evaluates mean and covariance of GP at grid of points on [0,1]
  # Inputs:
  # x, y: input and output values of data set
  # lam: smoothing parameter in RBF kernel
  # sig: error standard deviation of y
  # design: grid of points to evaluate the GP
  # Returns:
  # mean=posterior mean, vars=posterior variance, and design=evaluation points
  n <- length(y)
  Sigma <- matrix(0,nrow=n+nrow(design), ncol=n+nrow(design))
  
  all <- rbind(x, design)
  for (i in 1:nrow(Sigma)) {
    for (j in i:nrow(Sigma))
      # if ((y < 100 & (x >220 | x < -220)) | (y>=100 & (sqrt(y^2 + x^2) > 237))
      # then 3 pointer else 2 pointer
      
      Sigma[i,j] <- rbf.k(all[i,], all[j,], lam) -> Sigma[j,i]
  }
  S11 <- Sigma[1:n, 1:n]
  print(S11)
  S12 <- Sigma[1:n, (n+1):ncol(Sigma)]
  S21 <- Sigma[(n+1):ncol(Sigma), 1:n]
  S22 <- Sigma[(n+1):ncol(Sigma),(n+1):ncol(Sigma)]
  #sig shows up, how many shots at the grid point 
  # sig would be an n length vector
  inv <- S21%*%solve(S11+sig^2*diag(n))
  
  #y would be, at every grid point what is the average grid point
  mean <- inv%*%y
  cov <- S22-inv%*%S12
  vars <- diag(cov)
  return(list(mean=mean, vars=vars))
}



grid.a <- seq(-250,250,10)
grid.b <- seq(-10,350,10)
grid <- c()
grid.2 <- c()
grid.3 <- c()
p <- 0
for (i in 1:length(grid.a)) {
  for (j in 1:length(grid.b)) {
    #if three pointer
    if ((grid.b[j] < 100 & (grid.a[i] >220 | grid.a[i] < -220)) | (grid.b[j]>=100 &       (sqrt(grid.b[j]^2 + grid.a[i]^2) > 237))){
    grid.3 <- rbind(grid.3, c(grid.a[i], grid.b[j]))
    
    }
    else{
    grid.2 <- rbind(grid.2, c(grid.a[i], grid.b[j]))
    
    }
  }
}





#code that really does the work
start.time <- Sys.time()

xTwo <- cbind(x1Two,x2Two)
xThree <- cbind(x1Three, x2Three)

fit.2 <- gpreg(xTwo, yTwo, lam=47, sig=.5, design=grid.2)
fit.3 <- gpreg(xThree, yThree, lam=47, sig=.5, design=grid.3)

end.time <- Sys.time()
timeElapsed <- end.time-start.time

k <- 1
p <- 1
mean.fit <- matrix(0, nrow=length(grid.a), ncol=length(grid.b))
for (i in 1:length(grid.a)) {
  for (j in 1:length(grid.b)) {
    #We will have fit.2 and fit.3 and Ill need to check which of those fits has the means estimate for that point
    #Does grid.2 have this point? and if it does then grab fit.2$mean at that point
    if ((grid.b[j] < 100 & (grid.a[i] >220 | grid.a[i] < -220)) | (grid.b[j]>=100 &       (sqrt(grid.b[j]^2 + grid.a[i]^2) > 237))){
      mean.fit[i,j] <- fit.3$mean[k]
       k <- k + 1
    }
      else{
       mean.fit[i,j] <- fit.2$mean[p]
       p <- p + 1
      }
  }
}

plot(sunsgames$X_LOC, sunsgames$Y_LOC)


#Show the findings!
library(fields)
colorTable<- designer.colors(30, c( "blue","lightblue", "pink"  ,"red") )


persp(grid.a, grid.b, mean.fit, theta=30, phi=60)
image(grid.a, grid.b, mean.fit, col = colorTable)
timeElapsed

image.plot(grid.a, grid.b, mean.fit, col = colorTable)
#mean.fit

#Do not allow for negatives
h <- mean.fit
noZeroFit <- ifelse(h < 0, 0, h)
image.plot(grid.a, grid.b, noZeroFit, col = colorTable)
persp(grid.a, grid.b, noZeroFit, theta=30, phi=60)

```








for(i in 1:nrow(sunsgames)){
  if(sunsgames$X_LOC[i] == xLocs[counter] & sunsgames$Y_LOC[i] == yLocs[counter]){
    tempY[i] <- sunsgames$ppsAve[i]
    tempSig[i] <- 1/sqrt(sunsgames$n[i])
  }
  else{
    tempY[i] <- 0
    tempSig[i] <- 1000
    counter <- counter + 1
  }
}


  #sunsgames$shootingTeam[i] <- ifelse((sunsgames$home.shot[i] == TRUE & sunsgames$home.team[i] == 'PHX') | (sunsgames$home.shot[i] == FALSE & sunsgames$away.team[i] == 'PHX'), TRUE, FALSE)
