---
title: "Thesis"
author: "Adam Rees"
date: "October 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)
library(dplyr)
require(XML)
require(RCurl)
require(stringr)
require(png)
library(XML)
library(tidyr)

library(sp)
library(gstat)


library(rapportools)


```



```{r}

GameSchedule <-read.csv("~/Desktop/Thesis/ThesisBasketball/nba-full-schedule-2019-2020.csv")
GameSchedule <- separate(GameSchedule, "game_date", c("Month", "Day", "Year"), sep = "/")
GameSchedule <- GameSchedule %>% dplyr::select(away_team, home_team, Month, Day, Year)
TeamInfo <- read.csv("~/Desktop/Thesis/ThesisBasketball/TeamInfo", sep="")
TeamInfo
```

*IMPORTANT* Here, you choose what games you want to look at!
You always need to keep the last requirement that (Month is > 9 or Month < 3) so you do not look at games that were on the schedule but did not occur.
```{r}
gamesData <- GameSchedule %>% filter((home_team == "PHX" | away_team == "PHX") & (home_team == "GSW" | away_team == "GSW") & (Month > 9 | Month < 3))
gamesData
```


A function that turns a game time MM:SS into a numeric variable of seconds
```{r}
to.seconds <- function(time) {
colon <- gregexpr(":", time)[[1]]
if (colon>1) {
  min <- as.numeric(substr(time, 1,(colon-1)))
  sec <- as.numeric(substr(time,colon+1,47))
  time1 <- min*60+sec
}
if (colon==1) {
  time1 <- as.numeric(substr(time, 2, 5))
}
return(time1)
}
```


This code is trying to get all of the starters for each quarter... currently this does not work. For some quarters it gives 11 players.
Ideal output - a vector of length 30 that holds the 10 starters for each quarter.
```{r}
url <- getURL("https://sports.yahoo.com/nba/los-angeles-lakers-phoenix-suns-2019111221/?section=gamestream")

q1 <- gregexpr("End of 1st Quarter", url)[[1]][1]
q2 <- gregexpr("Halftime", url)[[1]]
q3 <- gregexpr("End of 3rd Quarter", url)[[1]][1]
q4 <- gregexpr("End of 4th Quarter", url)[[1]][1]
q2 <- q2[which(q2 > q1 & q2 <q3) ]
quarters <- c(q1,q2,q3,q4)


for(this.q in 2:4){
what.q <- this.q

qurl <- substr(url,quarters[what.q-1], quarters[what.q])

#Find out who recorded a stat in that quarter
player <- gregexpr("nba.p.", qurl)
ingame <- c()
for (i in 1:length(player[[1]])){
ingame[i] <- substr(qurl, player[[1]][i]+6, player[[1]][i]+9)
}


#Find out when the subs happened, and who entered and who exited

sub <- gregexpr("enters game", qurl)[[1]]
sub.times <- c()
sub.times.sec <- c()
for (i in 1:length(sub)) {
sub.times[i] <- substr(qurl, sub[i]+39, sub[i]+43)
if (substr(sub.times[i],2,2)==":")
sub.times[i] <- substr(sub.times[i],1,4)
sub.times.sec[i] <- to.seconds(sub.times[i])
}

enter <- c()
exit <- c()
for (i in 1:length(sub)) {
enter[i] <- ingame[which.max(1:length(player[[1]])*(player[[1]]<sub[i]))]
exit[i] <- ingame[which.max(1:length(player[[1]])*(player[[1]]<sub[i]))+1]
}


#If they never were recorded as entering or the first thing they did was exited, they must have started the Q

subbed <- unique(c(enter, exit))

start.quarter <- c()
for (i in 1:length(subbed)) {
  if (sum(enter==subbed[i])==0) {
    start.quarter <- c(start.quarter, subbed[i])
  }
  if (sum(enter==subbed[i])>0 & sum(exit==subbed[i])>0) {
    if (max(sub.times.sec[enter==subbed[i]]) < max(sub.times.sec[exit==subbed[i]]))
      start.quarter <- c(start.quarter, subbed[i])
  }
}

if (length(start.quarter) < 10) {
  ingame.u <- unique(ingame)
  for (i in 1:length(ingame.u)) {
    if (sum(ingame.u[i]==subbed)==0)
      start.quarter <- c(start.quarter, ingame.u[i])
  }
  
}
if(this.q == 2){
  sQ <- start.quarter
} else if(this.q == 3){
  tQ <- start.quarter
} else{
  fQ <- start.quarter
}

}

rbind(sQ,tQ,fQ)


```

https://sports.yahoo.com/nba/phoenix-suns-golden-state-warriors-201910309/?section=gamestream
```{r}

```




Getting the original data up. Pull in what URL you want and work from there
```{r}


fullData <- c()

numGames <- nrow(gamesData)

homeTeamAbrevs <- gamesData %>% dplyr::select(home_team)
awayTeamAbrevs <- gamesData %>% dplyr::select(away_team)
months <- gamesData %>% dplyr::select(Month)
days <- gamesData %>% dplyr::select(Day)

years <- gamesData %>% dplyr::select(Year)

#Go through every game in your selected dataset 
for(k in 1:numGames){

homeAbrev <- toString(homeTeamAbrevs[k,])
awayAbrev <- toString(awayTeamAbrevs[k,])

# a is just a placeholder variable to find other saved variables
a<- (TeamInfo %>% filter(Team == awayAbrev) %>% dplyr::select(FullLocation) )
awayteamLocation <- toString(a[1,])

a<- (TeamInfo %>% filter(Team == awayAbrev) %>% dplyr::select(FullName) )
awayteamName <- toString(a[1,])

a<- (TeamInfo %>% filter(Team == homeAbrev) %>% dplyr::select(FullLocation) )
hometeamLocation <- toString(a[1,])

a<- (TeamInfo %>% filter(Team == homeAbrev) %>% dplyr::select(FullName) )
hometeamName <- toString(a[1,])

y <- (years[k,])
m <- ifelse(nchar(months[k, ]) == 1, paste("0", months[k, ], sep = ""), months[k, ])
d <- ifelse(nchar(days[k, ]) == 1, paste("0", days[k, ], sep = ""), days[k, ])

teamNum <- toString(TeamInfo %>% filter(Team == homeAbrev) %>% dplyr::select(TeamNum))
if(as.numeric(teamNum) < 10){
  teamNum <- paste(0,teamNum, sep = "")
}

#use the information above to create a URL for every game in your dataset
createdURL <- paste("https://sports.yahoo.com/nba/", awayteamLocation, "-", awayteamName, "-", hometeamLocation, "-", hometeamName, "-", "20", y, m, d, teamNum, "/?section=gamestream",  sep= "")

url <- getURL(createdURL)


#who is the home team
l <- gregexpr("?section", url)[[1]][1]
homeTeam <- substr(url, l - 4, l-3)


#Character where JUMPBALL happened
postJump <- gregexpr("JUMPBALL", url)
#the string before the JUMPBALL - need to get the starters
starterStuff <- substr(url, 1, postJump[[1]][1])
players <- gregexpr("on_court", starterStuff)
homeAwayDivide <- gregexpr("home_lineup_order", starterStuff)

playerIDs <- c()
starters <- c()
playerChar <- c()
homeTeam <- c()

for(i in 1:length(players[[1]])){

#get all of the players IDS
playerChar[i] <- players[[1]][i]
playerIDs[i] <- substr(starterStuff, players[[1]][i] - 7, players[[1]][i] -4)

checkStarter <- substr(starterStuff, players[[1]][i] + 23, players[[1]][i] + 23)

#Identify if they are a starter or not
if(grepl(checkStarter, "0")){
  starters[i] <- FALSE 
  } else{
  starters[i] <- TRUE
  }

if(players[[1]][i] < homeAwayDivide){
  homeTeam[i] <- TRUE
} else{
  homeTeam[i] <- FALSE
}
}

startingLineups <- data.frame(playerIDs, starters, playerChar, homeTeam)
startingLineups

justStarters <- startingLineups %>% filter(starters == TRUE)
startingIDs <- c()
for(i in 1:nrow(justStarters)){
  startingIDs[i] <- toString(justStarters$playerIDs[i])
}
startingIDs

#We only want the data after the jump for the gameStream
data <- substr(url, postJump[[1]], nchar(url))


#Get all of the characters where shots were taken
shots <- gregexpr("SHOT", data)

newShots <- shots[[1]]
subs <- gregexpr("SUB", data)

#get rid of the NAs
newShots <- newShots[!is.na(newShots)]

#all of the characters where player is mentioned (could be for anything)
player <- gregexpr("player", data)
shotChar <- c()

#Match the player to the shooter
for (i in 1:length(newShots)){
  shotChar[i] <- player[[1]][which(player[[1]] > newShots[i] & player[[1]] < newShots[i]+47)]
}


shooterID <- c()


for(i in 1:length(shotChar)){
  shooterID[i] <- substr(data,shotChar[i]+9,shotChar[i]+12)
}

#data frame with every single shot and who shot it
shotLocations <- tibble(shotChar, shooterID)

# THE FOLLOWING IS CURRENTLY NOT WORKING
#Build a dataset for all of the subs
subChars <- append(0,subs[[1]])
allSubs <- data.frame(subChars)

numSubs <- length(allSubs[[1]])


q1 <- gregexpr("End of 1st Quarter", data)[[1]][1]
q2 <- gregexpr("Halftime", data)[[1]]
q3 <- gregexpr("End of 3rd Quarter", data)[[1]][1]
q4 <- gregexpr("End of 4th Quarter", data)[[1]][1]
q2 <- q2[which(q2 > q1 & q2 <q3) ]
quarters <- c(q1,q2,q3,q4)


quarterCounter <- 1

for(i in 1:numSubs){

  if(i == 1){
    allSubs$H1[1]<- startingIDs[1]
    allSubs$H2[1]<- startingIDs[2]
    allSubs$H3[1]<- startingIDs[3]
    allSubs$H4[1]<- startingIDs[4]
    allSubs$H5[1]<- startingIDs[5]
    allSubs$A1[1]<- startingIDs[6]
    allSubs$A2[1]<- startingIDs[7]
    allSubs$A3[1]<- startingIDs[8]
    allSubs$A4[1]<- startingIDs[9]
    allSubs$A5[1]<- startingIDs[10]
  }
  else if(allSubs[[1]][i] > q1 & quarterCounter == 1){
    quarterCounter <- 2
    i <- i - 1
    
    for(secondQSubs in 1:length(sQ)){
     sQ[secondQSubs] 
    }
    
  }
  else if(allSubs[[1]][i] > q2 & quarterCounter == 2){
    quarterCounter <- 3
    i <- i - 1
  }
  else if(allSubs[[1]][i] > q3 & quarterCounter == 3){
    quarterCounter <- 4
    i <- i - 1
  }

  else{
  
    #find the players that are getting subbed in and subbed out
findPlayer <- substr(data, allSubs$subChars[i], allSubs$subChars[i] + 150)
playerEnter <- gregexpr("enter_player", findPlayer)
playerLeave <- gregexpr("leave_player", findPlayer)

enterPlayer <- substr(findPlayer, playerEnter[[1]] + 15, playerEnter[[1]] + 18)
leavePlayer <- substr(findPlayer, playerLeave[[1]] + 15, playerLeave[[1]] + 18)
    
    if(allSubs$H1[i-1] == leavePlayer){
      allSubs$H1[i] <- enterPlayer
    }else{
      allSubs$H1[i] <- allSubs$H1[i-1]
    }
    if(allSubs$H2[i-1] == leavePlayer){
      allSubs$H2[i] <- enterPlayer
    }else{
      allSubs$H2[i] <- allSubs$H2[i-1]
    }
    if(allSubs$H3[i-1] == leavePlayer){
      allSubs$H3[i] <- enterPlayer
    }else{
      allSubs$H3[i] <- allSubs$H3[i-1]
    }
    if(allSubs$H4[i-1] == leavePlayer){
      allSubs$H4[i] <- enterPlayer
    }else{
      allSubs$H4[i] <- allSubs$H4[i-1]
    }
    if(allSubs$H5[i-1] == leavePlayer){
      allSubs$H5[i] <- enterPlayer
    }else{
      allSubs$H5[i] <- allSubs$H5[i-1]
    }
    if(allSubs$A1[i-1] == leavePlayer){
      allSubs$A1[i] <- enterPlayer
    }else{
      allSubs$A1[i] <- allSubs$A1[i-1]
    }
    if(allSubs$A2[i-1] == leavePlayer){
      allSubs$A2[i] <- enterPlayer
    }else{
    allSubs$A2[i] <- allSubs$A2[i-1]
    }
    if(allSubs$A3[i-1] == leavePlayer){
      allSubs$A3[i] <- enterPlayer
    }else{
      allSubs$A3[i] <- allSubs$A3[i-1]
    }
    if(allSubs$A4[i-1] == leavePlayer){
      allSubs$A4[i] <- enterPlayer
    }else{
      allSubs$A4[i] <- allSubs$A4[i-1]
    }
    if(allSubs$A5[i-1] == leavePlayer){
      allSubs$A5[i] <- enterPlayer
    }else{
      allSubs$A5[i] <- allSubs$A5[i-1]
    }
  
  }
    
}
#THE Code above is currently not fully working but the idea is to build a full dataset that has every sub in the game then I will use that to fill in who was on the court for every shot
    

#number of shots taken in the game
numShots <- nrow(shotLocations)

for(i in 1:numShots) {
  shotLocations$HomeTeam[i] <- homeTeam
  
  #get the long string that finds every action
  fullString <-
  substr(data, shotLocations$shotChar[i], shotLocations$shotChar[i] + 450)
  
  #get the time in the game
  timeChr <- gregexpr("clock", fullString)
  findTime <- substr(fullString, timeChr[[1]] + 8, timeChr[[1]] + 12)
  
  if (!substr(findTime, 1, 1) == "1" |
  substr(findTime, 1, 2) == "1:") {
  findTime <- substr(findTime, 1, 4)
  }
  if (substr(findTime, 1, 1) == ":") {
  findTime <- paste("0", substr(findTime, 1, 3), sep = "")
  }
  shotLocations$Time[i] <- findTime
  
  #Find what period/quarter it is in
  periodString <-
  substr(data, shotLocations$shotChar[i] - 50, shotLocations$shotChar[i])
  periodChr <- gregexpr("period", periodString)
  findPeriod <-
  substr(periodString, periodChr[[1]] + 9, periodChr[[1]] + 9)
  shotLocations$Period[i] <- findPeriod

  # Find the score for the home team
  homescoreChr <- gregexpr("home_score", fullString)
  findHomeScore <-
  substr(fullString, homescoreChr[[1]] + 13, homescoreChr[[1]] + 15)
  
  if (grepl(",", findHomeScore)) {
  findComma <- gregexpr(",", findHomeScore)
  findHomeScore <- substr(findHomeScore, 1, findComma[[1]] - 2)
  }
  x <- substr(findHomeScore, 3, 3)
  if (is.na(as.numeric(x)) & !is.empty(x)) {
  findHomeScore <- substr(findHomeScore, 1, 2)
  }
  shotLocations$HomeScore[i] <- findHomeScore
  
  #string that uses the data before the shot was taken .. fullString doesn't have that
  fStr <-
  substr(data, shotLocations$shotChar[i] - 25, shotLocations$shotChar[i])
  
  #Find the away score
  awayScoreChr <- gregexpr("away_score", fStr)
  findAwayScore <-
  substr(fStr, awayScoreChr[[1]] + 13, awayScoreChr[[1]] + 18)
  
  if (grepl(",", findAwayScore)) {
  findComma <- gregexpr(",", findAwayScore)
  findAwayScore <- substr(findAwayScore, 1, findComma[[1]] - 2)
  }
  shotLocations$AwayScore[i] <- findAwayScore
  
  #Find the baseline offset by getting a large string after the shot, finding where it says baseline offset and taking the number after it
  findBaseline <-
  substr(data, shotLocations$shotChar[i], shotLocations$shotChar[i] + 120)
  charBaseline <- gregexpr("baseline_offset", findBaseline)
  baseString <-
  substr(findBaseline, charBaseline[[1]] + 28, charBaseline[[1]] + 34)
  
  #baseline offset could be 0 to 4 characters - we want to just grab the number
  if (grepl(",", baseString)) {
  findComma <- gregexpr(",", baseString)
  baseString <- substr(baseString, 1, findComma[[1]] - 1)
  }
  
  #Same code but now for sideline offset
  findSideline <-
  substr(data, shotLocations$shotChar[i], shotLocations$shotChar[i] + 300)
  charSideline <- gregexpr("sideline_offset", findSideline)
  sideString <-
  substr(findSideline, charSideline[[1]] + 28, charSideline[[1]] + 33)
  
  if (grepl(",", sideString)) {
  findComma <- gregexpr(",", sideString)
  sideString <- substr(sideString, 1, findComma[[1]] - 1)
  }
  
  #they were characters but we want it to be a double
  shotLocations$baselineOffset[i] <- as.numeric(baseString)
  shotLocations$sidelineOffset[i] <- as.numeric(sideString)
  
  #find if the shot was made or missed
  findMakeMiss <-
  substr(data, shotLocations$shotChar[i], shotLocations$shotChar[i] + 460)
  makeMiss <- gregexpr("shot_made", findMakeMiss)
  makeMiss <-
  substr(findMakeMiss, makeMiss[[1]] + 12, makeMiss[[1]] + 12)
  if (makeMiss == "1") {
  shotLocations$MakeMiss[i] <- 1
  } else{
  shotLocations$MakeMiss[i] <- 0
  }
  
  #find if the shot was a 3 or a 2
  shotType <- gregexpr("points", findMakeMiss)
  shotType <-
  substr(findMakeMiss, shotType[[1]] + 9, shotType[[1]] + 9)
  shotLocations$shotType[i] <- as.double(shotType)
  
  #find what team the player was on
  findTeam <-
  substr(data, shotLocations$shotChar[i], shotLocations$shotChar[i] + 460)
  teamCharacter <- gregexpr("team", findTeam)
  team <-
  substr(findTeam, teamCharacter[[1]] + 7, teamCharacter[[1]] + 8)
  if (is.na(as.numeric(team))) {
  team <- substr(team, 1, 1)
  }
  shotLocations$Team[i] <- team
  
  #we now need to find what side of the basket the shot was taken. This is needed because the baseline offset is the same number for different sides of the basket
  shotLocations$sideBasket[i] <-
  substr(data, shotLocations$shotChar[i] + 62, shotLocations$shotChar[i] + 62)
  
  #use this to create a new variable plotting the X Location
  if (shotLocations$sideBasket[i] == 'R') {
  shotLocations$X_LOC[i] <-
  as.double(shotLocations$baselineOffset[i] * 500)
  } else{
  shotLocations$X_LOC[i] <-
  as.double(-1 * shotLocations$baselineOffset[i] * 500)
  }
  
  #also want the y location
  shotLocations$Y_LOC[i] <- shotLocations$sidelineOffset[i] * 940
  
}

#get the home and away teams
teams <- unique(shotLocations$Team)
#set the opposing team
shotLocations$OpposingTeam <-
ifelse(shotLocations$Team == teams[1], teams[2], teams[1])


#even after the for loop some X vals where characters - make sure they are doubles
shotLocations$X_LOC <- as.double(shotLocations$X_LOC)


#Filter out Free Throws
shotsNoFT <-
shotLocations %>% filter(!(
shotLocations$sidelineOffset == 0.1573 &
shotLocations$baselineOffset == 0.00
))


makes <- shotsNoFT %>% filter(shotsNoFT$MakeMiss == 1)
misses <- shotsNoFT %>% filter(shotsNoFT$MakeMiss == 0)


shotsNoFT$H1 <- ""
shotsNoFT$H2 <- ""
shotsNoFT$H3 <- ""
shotsNoFT$H4 <- ""
shotsNoFT$H5 <- ""
shotsNoFT$A1 <- ""
shotsNoFT$A2 <- ""
shotsNoFT$A3 <- ""
shotsNoFT$A4 <- ""
shotsNoFT$A5 <- ""

currentLineUp <- 1
maxSub <- length(allSubs[[1]])
maxShot <- length(shotsNoFT[[1]])

#find the players on the floor for every shot
for (i in 1:maxShot) {
#first, find what index of the subs players you want to use
while (currentLineUp < maxSub &
shotsNoFT$shotChar[i] > allSubs$subChars[currentLineUp + 1]) {
currentLineUp <- currentLineUp + 1
}


#update shotsNoFT to that index
shotsNoFT$H1[i] <- allSubs$H1[currentLineUp]
shotsNoFT$H2[i] <- allSubs$H2[currentLineUp]
shotsNoFT$H3[i] <- allSubs$H3[currentLineUp]
shotsNoFT$H4[i] <- allSubs$H4[currentLineUp]
shotsNoFT$H5[i] <- allSubs$H5[currentLineUp]
shotsNoFT$A1[i] <- allSubs$A1[currentLineUp]
shotsNoFT$A2[i] <- allSubs$A2[currentLineUp]
shotsNoFT$A3[i] <- allSubs$A3[currentLineUp]
shotsNoFT$A4[i] <- allSubs$A4[currentLineUp]
shotsNoFT$A5[i] <- allSubs$A5[currentLineUp]


}

fullData <- rbind(shotsNoFT, fullData)

}
fullData

min(fullData$baselineOffset)

```







Visualizations
```{r}
oneQuarter <- filter(fullData, Period == "4", winning == FALSE, lessFive < 5)

otherQ <- filter(fullData, Period != "4" | winning != FALSE | lessFive >= 5)

library(MASS)
oneQ <- kde2d(oneQuarter$X_LOC, oneQuarter$Y_LOC, lims = c(-250, 250, -20, 375))

persp(oneQ, theta = 45, phi = 55)
persp(otherQs, theta = 45, phi = 55)

differential <- differential * 1000

persp(oneQ$x, oneQ$y, differential, 
  theta = 30, phi = 30, expand = 0.19, scale=FALSE,
  shade=NA, col=colors[z.facet.range], border="grey80",
  box=FALSE, zlim = c(min(differential), max(differential)))

persp(differential, theta=45, phi=30)

persp(differential, theta=55, phi=30)

x <- seq(-250, 250, by = 25)
y <- seq(-20, 375, by = 25)


differential <- oneQ$z/sum(oneQ$z) - otherQs$z/sum(otherQs$z)

colorTable<- designer.colors(20, c( "blue","lightblue", "pink"  ,"red") )
image.plot(differential, col=colorTable)

#clim = c(-.012, .004)
persp(differential, theta = 15, phi= 40)

persp3D(oneQ$x, oneQ$y, differential, theta = 15, phi = 40, expand = 0.6, col = colorTable, colkey = TRUE, clim = c(-.012, .004))
```

```{r}



x1 <- currentGame$X_LOC
x2 <- currentGame$Y_LOC
y <- currentGame$pointsPerShot

#put the if .. 
rbf.k <- function(x,y,sigma)
  return(exp(-1/(2*sigma^2)*(sum((x-y)^2))))

gpreg <- function(x, y, lam, sig, design) {
  # Evaluates mean and covariance of GP at grid of points on [0,1]
  # Inputs:
  # x, y: input and output values of data set
  # lam: smoothing parameter in RBF kernel
  # sig: error standard deviation of y
  # design: grid of points to evaluate the GP
  # Returns:
  # mean=posterior mean, vars=posterior variance, and design=evaluation points
  n <- length(y)
  Sigma <- matrix(0,nrow=n+nrow(design), ncol=n+nrow(design))
  all <- rbind(x, design)
  for (i in 1:nrow(Sigma)) {
    for (j in i:nrow(Sigma))
      Sigma[i,j] <- rbf.k(all[i,], all[j,], lam) -> Sigma[j,i]
  }
  S11 <- Sigma[1:n, 1:n]
  S12 <- Sigma[1:n, (n+1):ncol(Sigma)]
  S21 <- Sigma[(n+1):ncol(Sigma), 1:n]
  S22 <- Sigma[(n+1):ncol(Sigma),(n+1):ncol(Sigma)]
  inv <- S21%*%solve(S11+sig^2*diag(n))
  mean <- inv%*%y
  cov <- S22-inv%*%S12
  vars <- diag(cov)
  return(list(mean=mean, vars=vars))
}



grid.a <- seq(-250,250,10)
grid.b <- seq(-10,490,10)
grid <- c()
for (i in 1:length(grid.a)) {
  for (j in 1:length(grid.b)) {
    grid <- rbind(grid, c(grid.a[i], grid.b[j]))
  }
}

start.time <- Sys.time()
x <- cbind(x1,x2)
fit <- gpreg(x, y, lam=30, sig=.5, design=grid)
end.time <- Sys.time()
end.time-star.time

k <- 1
mean.fit <- matrix(0, nrow=length(grid.a), ncol=length(grid.b))
for (i in 1:length(grid.a)) {
  for (j in 1:length(grid.b)) {
    mean.fit[i,j] <- fit$mean[k]
    k <- k + 1
  }
}
persp(grid.a, grid.b, mean.fit, theta=60, phi=60)
image(grid.a, grid.b, mean.fit)

```

Error in solve.default(S11 + sig^2 * diag(n)) : 'a' is 0-diml

-250
[1] -28.05
[1] 250
[1] 744.94










